---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# unhcrdown

<!-- badges: start -->
[![R-CMD-check](https://github.com/vidonne/unhcrdown/workflows/R-CMD-check/badge.svg)](https://github.com/vidonne/unhcrdown/actions)
<!-- badges: end -->

The **unhcrdown** package provides a set of templates following [UNHCR Brand](https://www.unhcr.org/brand) recommendations. The goal of this package is to ease and speed up the creation of reports, presentation and website while promoting the UNHCR visual identity. 

## Installation

This package is not on yet on CRAN and to install it, you will need the remotes package.

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("vidonne/unhcrdown")
```

## Content

A package with all **necessary templates** to quickly create UNHCR branded reports, presentations and more:

1. Powerpoint presentation
2. Xaringan presentation
3. HTML paged report that can be exported to PDF document
    - `paged_report`, advanced report template including page cover, table of content, back-cover and more.
    - `paged_simple`, simple document template to create quick reports, updates, etc.

**Upcoming templates:**

1. Word
2. HTML
3. [Distill](https://rstudio.github.io/distill/)
4. [Rolldown](https://github.com/yihui/rolldown)

```{r child="man/rmdfragments/unhcrverse.Rmd"} 
```
